### 2020-03-16 Rmd/World_Map_Breeding_Systems.Rmd
Playing with the coordinates to show the plot nicely

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA

setwd("~/R_Projects/Reproductive Traits")
Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

@@

@@

p <- ggplot(world, aes(long, lat)) +
  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
                     data = data_merged_sub, cols = colnames(data_merged_sub[,c(7:9)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub[,c(7:9)]),
                       labels = c("Hermaphroditism", "Dioecy", "Monoecy"),
                       values = c("Hermaphroditism" = "#4DAF4A",
                                  "Monoecy" = "#984EA3",
                                  "Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
  caption = "",fill = NULL) +
  theme(legend.position = c(0.21, 0.009),
        legend.justification = c(1, 0),
        axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm"))

>>>>

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA
setwd("~/R_Projects/Reproductive Traits")
Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

@@

data_merged_sub_ord <- data_merged_sub[order(data_merged_sub$Id_number),]
#Move coordinates manually to see all points (Improving plot visualization)
#Manual jitter
data_merged_sub_ord$Id_number <- seq(1, length(data_merged_sub_ord$Id_number))
#Fixing New Zealand pies
data_merged_sub_ord[19,4] <- -29
data_merged_sub_ord[19,3] <- 180
data_merged_sub_ord[20,4] <- -40
data_merged_sub_ord[20,3] <- 180
data_merged_sub_ord[21,4] <- -51
data_merged_sub_ord[21,3] <- 180

#Fixing Galapagos pies
data_merged_sub_ord[18,4] <- -6
data_merged_sub_ord[27,4] <- 5
#Fixing Galapagos pies
data_merged_sub_ord[13,4] <- -14
data_merged_sub_ord[17,4] <- -25
#Fixing Denmark pies
data_merged_sub_ord[3,4] <- 70
data_merged_sub_ord[4,4] <- 60
data_merged_sub_ord[7,4] <- 50

@@

p <- ggplot(world, aes(long, lat)) +
  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
                       labels = c("Hermaphroditism", "Dioecy", "Monoecy"),
                       values = c("Hermaphroditism" = "#4DAF4A",
                                  "Monoecy" = "#984EA3",
                                  "Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
  caption = "",fill = NULL) +
  theme(legend.position = c(0.21, 0.009),
        legend.justification = c(1, 0),
        axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm"))+geom_segment(data = data_merged_sub_ord, 
  aes(x = 174, y = -28, xend = 170, yend = -45), color = "lightblue", size = 0.3, alpha = 0.2,
  arrow = arrow(length = unit(0.08, "inches")))
